### 2015-03-16 Projects/DelCo_2014/Report/Hose_Tests/DelCo_Hose_Tests_2014.tex
DelCo_Hose_Tests: Updated report with Test 16/17 figures and tables, added comments to plotting scripts

Water flowrate was measured with a pressure and flow meter combination shown in Fig. \ref{fig:flow_meter}. The meter consists of a section of 6.35 cm (2.5 inch) cast aluminum pipe with a 0–4.1 MPa (0-600 psi) pressure transducer and a paddlewheel type flow sensor with a range of 0 to 4800 lpm (1250 gpm). The pressure transducer and paddlewheel both connect to the battery operated control box where the pressure transducer voltage is converted to a pressure and the paddlewheel pulse count is converted to a volumetric flow rate. The manufacturer reports a $\pm5$\% calibration expanded uncertainty for the flow sensor and $\pm3$\%  for the pressure sensor \cite{Akron}. The pressure transducer was calibrated with a known analog pressure gauge. The flow meter was calibrated by capturing water over time and measuring that mass of water to determine the flowrate. The total expanded uncertainty was estimated at $\pm10$\%.

@@

\subsubsection{Handline Experimental Procedure}
\label{sec:Handline_Procedure}
Two sets of experiments, Tests 18 and 19, involved flowing water in different stream patterns from a 1$\frac{3}{4}$" handline equipped with a combination nozzle. Each hose stream was flowed in four different patterns: a fixed position, a sweeping pattern, a clockwise pattern, and a counter clockwise pattern.

@@

\begin{figure}[!ht]
\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_18_West_063014_BDP_A10_Avg}
\caption{Average Velocity of Stairwell Door, Test 18, All Streams}
\label{fig:Test_18_BDP_A10_Avg_All}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_19_West_063014_BDP_A10_Avg}
\caption{Average Velocity of Stairwell Door, Test 19, All Streams}
\label{fig:Test_19_BDP_A10_Avg_All}
\end{figure}

@@

\begin{table}[!ht]
\caption{Average Air Velocity Through Stairwell Door for All Hose Stream and Application Pattern Combinations for Tests 18 and 19}
\begin{tabular}{|l|l|c|c|c|c|}
\hline
\multicolumn{5}{|c|}{Test 18} \\ \hline
\textbf{Stream} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular} \\ \hline
\textit{Straight} & -0.17 & 0.48 & 0.65 & 0.63 \\ \hline
\textit{Narrow Fog} & 0.41 & 1.02 & 0.79 & 0.99 \\ \hline
\textit{Wide Fog} & 0.93 & 0.90 & 0.91 & 0.75 \\ \hline
\multicolumn{5}{|c|}{Test 19} \\ \hline
\textbf{Stream} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular} \\ \hline
\textit{Straight} & -0.05 & 0.47 & 0.67 & 0.62 \\ \hline
\textit{Narrow Fog} & 1.23 & 1.18 & 1.14 & 1.22 \\ \hline
\textit{Wide Fog} & 0.96 & 0.67 & 0.89 & 0.93 \\ \hline
\end{tabular}
\label{table:Tests_18_19_BDP_A10_Avgs}
\end{table}

\begin{table}[!ht]
\caption{Average Air Velocity Through \nth{2} Level Double Door for All Hose Stream and Application Pattern Combinations for Tests 18 and 19}
\begin{tabular}{|c|c|c|c|c|}
\hline
\multicolumn{5}{|c|}{Test 18} \\ \hline
\textbf{Stream} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular} \\ \hline
\textit{Straight} & -0.43 & 1.75 & 2.46 & 2.40 \\ \hline
\textit{Narrow Fog} & 1.34 & 3.61 & 2.55 & 3.48 \\ \hline
\textit{Wide Fog} & 3.02 & 3.22 & 3.06 & 2.57 \\ \hline
\multicolumn{5}{|c|}{Test 19} \\ \hline
\textbf{Stream} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular} \\ \hline
\textit{Straight} & 0.20 & 1.60 & 2.47 & 2.10 \\ \hline
\textit{Narrow Fog} & 4.26 & 3.48 & 3.49 & 3.66 \\ \hline
\textit{Wide Fog} & 3.31 & 2.60 & 3.13 & 3.19 \\ \hline
\end{tabular}
\label{table:Tests_18_19_BDP_A13_Avgs}
\end{table}

\subsubsection{Clockwise vs. Counterclockwise Rotation}

\begin{figure}[!ht]
\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_18_West_063014_BDP_A10_Avg_CW_vs_CCW}
\caption{Average Velocity of Stairwell Door, Test 18, All Streams, CW vs. CCW}
\label{fig:Test_18_BDP_A10_Avg_CW_vs_CCW}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_19_West_063014_BDP_A10_Avg_CW_vs_CCW}
\caption{Average Velocity of Stairwell Door, Test 19, All Streams, CW vs. CCW}
\label{fig:Test_19_BDP_A10_Avg_CW_vs_CCW}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_18_West_063014_BDP_A13_Avg_CW_vs_CCW}
\caption{Average Velocity of \nth{2} Level Double Door, Test 18, All Streams, CW vs. CCW}
\label{fig:Test_18_BDP_A13_Avg_CW_vs_CCW}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_19_West_063014_BDP_A13_Avg_CW_vs_CCW}
\caption{Average Velocity of \nth{2} Level Double Door, Test 19, All Streams, CW vs. CCW}
\label{fig:Test_19_BDP_A13_Avg_CW_vs_CCW}
\end{figure}

>>>>

Water flowrate was measured with a pressure and flow meter combination shown in Fig. \ref{fig:flow_meter}. The meter consists of a section of 6.35 cm (2.5 inch) cast aluminum pipe with a 0-4.1 MPa (0-600 psi) pressure transducer and a paddlewheel type flow sensor with a range of 0 to 4800 lpm (1250 gpm). The pressure transducer and paddlewheel both connect to the battery operated control box where the pressure transducer voltage is converted to a pressure and the paddlewheel pulse count is converted to a volumetric flow rate. The manufacturer reports a $\pm5$\% calibration expanded uncertainty for the flow sensor and $\pm3$\%  for the pressure sensor \cite{Akron}. The pressure transducer was calibrated with a known analog pressure gauge. The flow meter was calibrated by capturing water over time and measuring that mass of water to determine the flowrate. The total expanded uncertainty was estimated at $\pm10$\%.

@@

\subsubsection{Handline Experimental Procedure}
\label{sec:Handline_Procedure}
Two sets of experiments, Tests 18 and 19, involved flowing water in different stream patterns from a 1.75" handline equipped with a combination nozzle. Each hose stream was flowed in four different patterns: a fixed position, a sweeping pattern, a clockwise pattern, and a counter clockwise pattern.

@@

\subsection{Monitor Nozzle Experiments}

Figures \ref{fig:Test_16_BDP_A10_Avg_All}-\ref{fig:Test_17_BDP_A13_Avg_All} contain plots of the average velocity through the stairwell door and \nth{2} level, north side, west double door, measured by the bi-directional probes in each doorway for the two application locations and three hose stream patterns for Tests 16 and 17.

\begin{figure}[!ht]
\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_16_West_063014_BDP_A10_Avg}
\caption{Average Velocity through Stairwell Door, Test 16, All Streams}
\label{fig:Test_16_BDP_A10_Avg_All}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_16_West_063014_BDP_A13_Avg}
\caption{Average Velocity through \nth{2} Level, North Side, West Double Door, Test 16, All Streams}
\label{fig:Test_16_BDP_A13_Avg_All}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_17_West_063014_BDP_A13_Avg}
\caption{Average Velocity through Stairwell Door, Test 17, All Streams}
\label{fig:Test_17_BDP_A10_Avg_All}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_17_West_063014_BDP_A13_Avg}
\caption{Average Velocity through \nth{2} Level, North Side, West Double Door, Test 17, All Streams}
\label{fig:Test_17_BDP_A13_Avg_All}
\end{figure}

\begin{table}[!ht]
\caption{Average Air Velocity Through Stairwell Door for All Hose Stream and Application Location Combinations for Tests 16 and 17}
\begin{tabular}{|l|l|c|c|c|c|}
\hline
\multicolumn{3}{|c|}{Test 16 Avg. Velocities (m/s)} \\ \hline
\textbf{Stream} & \textbf{Near} & \textbf{Far} \\ \hline
\textit{Straight} & 0.84 & 0.94 \\ \hline
\textit{Narrow Fog} & 1.41 & 1.00 \\ \hline
\textit{Wide Fog} & 1.23 & 1.37 \\ \hline
\multicolumn{3}{|c|}{Test 17 Avg. Velocities (m/s)} \\ \hline
\textbf{Stream} & \textbf{Near} & \textbf{Far} \\ \hline
\textit{Straight} & 0.73 & 0.69 \\ \hline
\textit{Narrow Fog} & 0.75 & 0.75 \\ \hline
\textit{Wide Fog} & 0.88 & 0.71 \\ \hline
\end{tabular}
\label{table:Tests_16_17_BDP_A10_Avgs}
\end{table}

\begin{table}[!ht]
\caption{Average Air Velocity Through \nth{2} Level Double Door for All Hose Stream and Application Pattern Combinations for Tests 16 and 17}
\begin{tabular}{|l|l|c|c|c|c|}
\hline
\multicolumn{3}{|c|}{Test 16 Avg. Velocities (m/s)} \\ \hline
\textbf{Stream} & \textbf{Near} & \textbf{Far} \\ \hline
\textit{Straight} & 2.82 & 3.10 \\ \hline
\textit{Narrow Fog} & 4.39 & 3.26 \\ \hline
\textit{Wide Fog} & 3.92 & 4.37 \\ \hline
\multicolumn{3}{|c|}{Test 17 Avg. Velocities (m/s)} \\ \hline
\textbf{Stream} & \textbf{Near} & \textbf{Far} \\ \hline
\textit{Straight} & 2.66 & 2.33 \\ \hline
\textit{Narrow Fog} & 2.58 & 2.68 \\ \hline
\textit{Wide Fog} & 3.14 & 2.76 \\ \hline
\end{tabular}
\label{table:Tests_16_17_BDP_A13_Avgs}
\end{table}

\subsection{Handline Experiments}

Figures \ref{fig:Test_18_BDP_A10_Avg_All}-\ref{fig:Test_19_BDP_A13_Avg_All} contain plots of the average velocity through the stairwell door and \nth{2} level, north side, west double door, measured by the bi-directional probes in each doorway for the four application patterns and three hose stream patterns for Tests 18 and 19.

\begin{figure}[!ht]
\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_18_West_063014_BDP_A10_Avg}
\caption{Average Velocity through Stairwell Door, Test 18, All Streams}
\label{fig:Test_18_BDP_A10_Avg_All}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_18_West_063014_BDP_A13_Avg}
\caption{Average Velocity through \nth{2} Level, North Side, West Double Door, Test 18, All Streams}
\label{fig:Test_18_BDP_A13_Avg_All}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_19_West_063014_BDP_A10_Avg}
\caption{Average Velocity through Stairwell Door, Test 19, All Streams}
\label{fig:Test_19_BDP_A10_Avg_All}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_19_West_063014_BDP_A13_Avg}
\caption{Average Velocity through \nth{2} Level, North Side, West Double Door, Test 19, All Streams}
\label{fig:Test_19_BDP_A13_Avg_All}
\end{figure}

@@

\begin{table}[!ht]
\caption{Average Air Velocity Through Stairwell Door for All Hose Stream and Application Pattern Combinations for Tests 18 and 19}
\begin{tabular}{|l|l|c|c|c|c|}
\hline
\multicolumn{5}{|c|}{Test 18 Avg. Velocities (m/s)} \\ \hline
\textbf{Stream} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular} \\ \hline
\textit{Straight} & -0.17 & 0.48 & 0.65 & 0.63 \\ \hline
\textit{Narrow Fog} & 0.41 & 1.02 & 0.79 & 0.99 \\ \hline
\textit{Wide Fog} & 0.93 & 0.90 & 0.91 & 0.75 \\ \hline
\multicolumn{5}{|c|}{Test 19 Avg. Velocities (m/s)} \\ \hline
\textbf{Stream} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular} \\ \hline
\textit{Straight} & -0.05 & 0.47 & 0.67 & 0.62 \\ \hline
\textit{Narrow Fog} & 1.23 & 1.18 & 1.14 & 1.22 \\ \hline
\textit{Wide Fog} & 0.96 & 0.67 & 0.89 & 0.93 \\ \hline
\end{tabular}
\label{table:Tests_18_19_BDP_A10_Avgs}
\end{table}

\begin{table}[!ht]
\caption{Average Air Velocity Through \nth{2} Level Double Door for All Hose Stream and Application Pattern Combinations for Tests 18 and 19}
\begin{tabular}{|c|c|c|c|c|}
\hline
\multicolumn{5}{|c|}{Test 18 Avg. Velocities (m/s)} \\ \hline
\textbf{Stream} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular} \\ \hline
\textit{Straight} & -0.43 & 1.75 & 2.46 & 2.40 \\ \hline
\textit{Narrow Fog} & 1.34 & 3.61 & 2.55 & 3.48 \\ \hline
\textit{Wide Fog} & 3.02 & 3.22 & 3.06 & 2.57 \\ \hline
\multicolumn{5}{|c|}{Test 19 Avg. Velocities (m/s)} \\ \hline
\textbf{Stream} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular} \\ \hline
\textit{Straight} & 0.20 & 1.60 & 2.47 & 2.10 \\ \hline
\textit{Narrow Fog} & 4.26 & 3.48 & 3.49 & 3.66 \\ \hline
\textit{Wide Fog} & 3.31 & 2.60 & 3.13 & 3.19 \\ \hline
\end{tabular}
\label{table:Tests_18_19_BDP_A13_Avgs}
\end{table}

Notice, there is a significant difference between the average air velocity caused by the fixed straight stream and the velocity caused by the narrow and wide fog streams; the velocities for the narrow and wide fog were always significantly higher than the velocity of the fixed stream. It was only when the hose began to move around that the air velocity through the doorways for the straight stream approached the air velocities associated with the narrow and wide fogs for the corresponding pattern. However, the straight stream hose pattern always resulted in the lowest average air velocity through each doorway for the three different hose streams at each of the four application patterns.

Another important result shown in Figures \ref{fig:Test_18_BDP_A10_Avg_All} and \ref{fig:Test_19_BDP_A10_Avg_All} and in Tables \ref{table:Tests_18_19_BDP_A10_Avgs} and \ref{table:Tests_18_19_BDP_A13_Avgs} is that there is statistically no significant difference in the amount of air flow through the doorways between rotating the hoseline in the clockwise and counter clockwise directions for the three hose streams tested.

%\begin{figure}[!ht]
%\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_18_West_063014_BDP_A10_Avg_CW_vs_CCW}
%\caption{Average Velocity of Stairwell Door, Test 18, All Streams, CW vs. CCW}
%\label{fig:Test_18_BDP_A10_Avg_CW_vs_CCW}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_19_West_063014_BDP_A10_Avg_CW_vs_CCW}
%\caption{Average Velocity of Stairwell Door, Test 19, All Streams, CW vs. CCW}
%\label{fig:Test_19_BDP_A10_Avg_CW_vs_CCW}
%\end{figure}
%
%\clearpage
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_18_West_063014_BDP_A13_Avg_CW_vs_CCW}
%\caption{Average Velocity of \nth{2} Level Double Door, Test 18, All Streams, CW vs. CCW}
%\label{fig:Test_18_BDP_A13_Avg_CW_vs_CCW}
%\end{figure}
%
%\clearpage
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_19_West_063014_BDP_A13_Avg_CW_vs_CCW}
%\caption{Average Velocity of \nth{2} Level Double Door, Test 19, All Streams, CW vs. CCW}
%\label{fig:Test_19_BDP_A13_Avg_CW_vs_CCW}
%\end{figure}
%
%\clearpage
